\section{Research Experience}

\begin{tabularx}{\textwidth}{D|I}

\emph{Present}  & \textsc{DarkSide} Collaboration, \UCD \\
\textsc{July 2018} & \textit{PI: Prof. Emilija Pantic} \\
& {\footnotesize \hl{FIXME} Worked on experimental design, data acquisition system development, hardware development, and detector commissioning for ARIS-ER. Ran Monte Carlo simulations in \textsc{Geant4} for the design of \textsc{DarkSide-20k}, with a focus on backgrounds and optical modeling. Contributed to the analysis of data collected by DarkSide-50.} \\

\arrayrulecolor{white}\hline \hline \hline \arrayrulecolor{black}

%\textsc{June 2018} \textsc{Jan 2016} & \textsc{Super Cryogenic Dark Matter Search (SuperCDMS)} Collaboration, \textbf{University of Minnesota} \\
\textsc{June 2018} & \textsc{Cryogenic Dark Matter Search (CDMS)} Collaboration, \UMN \\
\textsc{Jan 2016} & \textit{PI: Prof. Priscilla Cushman} \\
& {\footnotesize Developed components for the active neutron veto of the proposed \textsc{SuperCDMS SNOLAB} detector. Worked on loading gadolinium into plastic scintillator and characterized sample properties.} \\

\arrayrulecolor{white}\hline \hline \hline \arrayrulecolor{black}

\textsc{June 2017}  & \textsc{Light Dark Matter eXperiment (LDMX)} Collaboration, \UMN \\
\textsc{Jan 2017} & \textit{PI: Prof. Jeremiah Mans} \\
& {\footnotesize Measured the event discrimination efficiency of thin plastic scintillator sheets for the \textsc{LDMX} experiment.} \\

\arrayrulecolor{white}\hline \hline \hline \arrayrulecolor{black}

\textsc{June 2016} & \textsc{Greven} Research Group, \UMN \\
\textsc{Sept 2015} & \textit{PI: Prof. Martin Greven} \\
& {\footnotesize Grew and analyzed Hg1201 crystals to collect data on possible mechanisms behind high-temperature superconductivity. Tasks included crystal growth in conventional box furnaces, sample annealing, and measurements of susceptibility using a MPMS instrument.} \\

\end{tabularx}